The dependence of spiral disk morphology on the mass-star formation relation

### 2014-07-25 mainsequence_morph.tex
Remade bar, arms winding plots

% Figure: example images of: 1-5 arms, plus arm tightness, plus barred vs. non-barred.

@@

It should also be mentioned that the galaxies in GZ2 flagged as a function of pitch angle are not representative of the true vote distribution. The raw numbers in Figure~\ref{fig-winding} suggest that most spiral galaxies are either tightly or loosely wound. In fact, the plurality classification for most galaxies is for medium-winding; the spread in votes is typically large, though, and so users rarely agree on the medium option at the 80\% level which sets the flag. Plotting the same star-forming main sequence diagram as a function of $p_{medium}$, which more accurately tracks the pitch angle distribution, shows no significant deviations from the main sample. {\color{red}HAVEN'T ACTUALLY DONE THIS!}

Figure~\ref{fig-bar}: $M_\star-SFR$ for barred vs unbarred \\
Figure~\ref{fig-mergers}: $M_\star-SFR$ for merging galaxies \citet{dar10a} \\

\begin{figure*}
\includegraphics[angle=0,width=7.0in]{figures/ms_bar.pdf}
\caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the detection of a galactic bar. 
\label{fig-bar}}
\end{figure*}

@@

There is no significant difference between any of the morphological categories explored. Statistical test for how not different the categories are.

@@

The biggest forcing we can think of for the system is a major merger. Even that doesn't push it too far off the main sequence, indicating short timescales and higher levels of feedback.

We know that this is true at low redshift, but not at higher redshift. \citet{rod11} show a significant increase at $1.5<z<2.5$, likely due to the \emph{higher gas fraction} in galaxies at these redshifts. Also significant difference in disks at low/high redshift when using disk surface density instead of mass \citep{dad10}. \citet{elb11} show that ``compact'' galaxies lie significantly off the SFR-MS using {\it Herschel} data. In the local Universe, the green peas are the only galaxies that significantly exceed the main sequence, as evidenced by their sSFR \citep{car09}.

>>>>

% Figure: example images?

@@

It should also be mentioned that the galaxies in GZ2 flagged as a function of pitch angle are not representative of the true vote distribution. The raw numbers in Figure~\ref{fig-winding} suggest that most spiral galaxies are either tightly or loosely wound. In fact, the plurality classification for most galaxies is for medium-winding; the spread in votes is typically large, though, and so users rarely agree on the medium option at the 80\% level which sets the flag. Plotting the same star-forming main sequence diagram as a function of $p_{medium}$, which more accurately tracks the pitch angle distribution, also closely follows the main star-forming main sequence. % Figure ms_arms_winding_weighted_pmed.pdf shows this. Not sure if we need to put it in the paper?

\begin{figure*}
%\includegraphics[angle=0,width=7.0in]{figures/ms_bar.pdf}
\includegraphics[angle=0,width=7.0in]{figures/ms_bar_contour.pdf}
\caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the detection of a galactic bar. 
\label{fig-bar}}
\end{figure*}

Finally, we examine the effect of a large-scale galactic bar on the star-forming main sequence. This sample is significantly larger than those including spiral arm morphology, since the classification is at a higher level in the GZ2 tree and has only two choices; this results in a higher percentage of consensus classifications that set the flag. Figure~\ref{fig-bar} shows the star-forming main sequence for both barred and unbarred galaxies. Although the fraction of barred galaxies potentially varies as a function of stellar mass \citep{mas11c}, both the linear fits and ranges of the sub-populations are consistent with all star-forming galaxies. In other words, the presence of a bar does not affect the galaxy's position on the star-forming main sequence.

@@

There is no significant difference between any of the morphological categories explored. Statistical test for how ``not different'' the categories are.

@@

The biggest forcing we can think of for the system is a major merger. Even that doesn't push it too far off the main sequence, indicating short timescales and higher levels of feedback. Figure~\ref{fig-mergers} shows the relation for 3,003~systems of merging galaxies \citep{dar10a}. For these systems, there is a small increase in the offset of the $M_\star-SFR$ relation, but none in the slope. The difference is $\sim0.2$~dex, an increase of only $\sim70\%$ in star-formation rate for a given mass. There are a very small number of galaxies whose star formation rates lie more than an order of magnitude above the standard relation, but the numbers are too small to make a significant contribution to the SFR density of the local Universe.

These results confirm the trend in specific star formation rate seen by \citet{dar10}. We know that this is true at low redshift, but not at higher redshift. \citet{rod11} show a significant increase at $1.5<z<2.5$, likely due to the \emph{higher gas fraction} in galaxies at these redshifts. Also significant difference in disks at low/high redshift when using disk surface density instead of mass \citep{dad10}. \citet{elb11} show that ``compact'' galaxies lie significantly off the SFR-MS using {\it Herschel} data. In the local Universe, green pea galaxies are the only objects that significantly exceed the main sequence, as evidenced by their sSFR \citep{car09}.
